\begin{biblio}
\bibitem{Anderson-May}
R.M.Anderson, and R.M.May,Infectious Diseases of Humans. Dynamics and Control, Oxford UniversityPress, 1992.
\bibitem{Bailey}
 N.J.T.Bailey,The mathematical theory of infectious diseases and its application, Griffin, 1975.
\bibitem{Uemov}
А. И. Уёмов Логические основы метода моделирования, М.: Мысль, 1971. — 311 с, c.48
\bibitem{SSE.Vocabulary}
ISO/IEC/IEEE 24765:2010 Systems and software engineering — Vocabulary
IEEE Std 1233—1998 (R2002) IEEE Guide for Developing System Requirements Specifications
\bibitem{SI.SIS.SIR}
Mathematical Modeling of Epidemics: basic SI/SIS/SIR models explained // [Электронный доступ: https://www.youtube.com/watch?v=IXkr0AsEh1w\&t=2461s]
\bibitem{Abou-Ismail}
 Abou-Ismail A. Compartmental Models of the COVID-19 Pandemic for Physicians and
Physician-Scientists  //  SN  Compr  Clin  Med.  –  2020.  –  1-7.  [Электронный  доступ:
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7270519]
\bibitem{Giordano}
 Giordano G. et al. Modelling the COVID-19 epidemic and implementation of population-
wide interventions in Italy // Nature Medicine. – 2020. – P. 1-6.
\bibitem{Koehler}
 Koehler  J.  et  al.  Robust  and  optimal  predictive  control  of  the  COVID-19  outbreak  //
arXiv preprint arXiv:2005.03580. – 2020.

\bibitem{RecoveredTests} L.  Lan  et  al.,   “Positive  RT-PCR  test  results  in  patients  recovered  from  COVID-19”,JAMA,  2020,doi:10.1001/jama.2020.2783.
\bibitem{AsymptomaticCarrierTransmission} Y.    Bai    et    al.,“Presumed    asymptomatic    carrier    transmission    of    COVID-19”,JAMA,    2020,doi:10.1001/jama.2020.2565
\end{biblio} 
